---
title: "Week 9, Day 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# There is one change to our data from Tuesday. We have a created a new
# variable: `poverty_n`, where the "n" stands for "normalized." To normalize data
# is to subtract the mean and divide by the standard deviation. This can be
# helpful. The coefficient to such a variable can be interpreted as a comparison
# between two groups, separated by a one standard deviation of the poverty
# measure.


week_9 <- kenya %>% 
  rename(reg_chg = reg_byrv13) %>% 
  filter(treatment %in% c("control", "local")) %>% 
  droplevels() %>% 
  mutate(poverty_n = (poverty - mean(poverty))/sd(poverty)) %>% 
  select(poll_station, reg_chg, treatment, poverty_n, poverty)
  
```


## Scene 1

**Prompt:** Let's create a new model. Consider `reg_chg` as a function of `treatment`, `poverty_n` and the interaction between the two.

* Write the math for this model.

$reg\_chg = \beta_0 + \beta_1 * local_i + \beta_2 poverty\_n_i_i + \beta_3 local_i poverty\_n_i + \epsilon_i$

* Describe the population for which you are creating the model.

kenya elctions between time data is recorded

* Fit the  model and interpret the coefficients. Focus on the coefficient of the interaction term.

intercept: when other vars are at zero. mean of original dataset. .04 is the average regustration change fo comunitie where poverty rate is the mean 

treatmentlocal: effect of being treated on registration change

poverty_n: slope for povrty when treatment local is 0 because slope for pov n is 0 when ... the interaction term is telling us that there is a lager effect of poverty in teh treattment groups than the relationshipbetween poverty and reg change in teh control groups 

var itself is not the slope for the var not included 

```{r}
fit <- stan_glm(formula = reg_chg ~ treatment*poverty_n,
          data = week_9,
          refresh = 0,
          family = gaussian())
print(fit, digits = 4)

```


## Scene 2

**Prompt:** Let's begin with a question from Kenyan President Uhuru Kenyatta:

*Consider the polling station 007/001. What are the chances of an increase in registration of 4% if I were to give it the local treatment in January?*

Write a sentence or two for each of these topics:

* What would Wisdom suggest about the use of the `kenya` data to answer this question?

wisdom would indivate thet the data is pproproate to answering teh question aboce with the study being conducted in JAnuary and reg_chg approprately mapping changes in voter registration relative to treatment.

* Describe the ideal Preceptor Table.

would have reg change value for multiple observations as well as their sex and 
local and control values for eah polling station, to approriately note the treatment as wella s poverty 
ideally, this table would include each row as a difff polling station, would be looking at treatment and control status fro eachstation adn its poverty n level


* Graph the posterior probability distribution `reg_chg` if polling station 007/001 were to be assigned treatment in January.

* Answer the President's question.

```{r}

newobs <- tibble(treatment = "Control", poverty_n = -1.60835093)

# using posterior [redict becuae we are working with an individual]
pp <- posterior_predict(fit, new_data = newobs) %>%
  as_tibble() %>%
  mutate_all(as.numeric)

pp %>%
  ggplot(aes(x = `1`)) +
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 alpha = 0.5,
                 bins = 100,
                 color = "darkslateblue",
                 fill = "lavender") +
  labs(title = "Posterior Predictive Distribution",
       subtitle = "registation change at polling station 007/001 under treatment",
       x = "Change in Attitude",
       y = "Probability") +
  scale_y_continuous(labels=scales::percent_format()) + 
  theme_classic()

sum(pp$`1` > 0.04)/length(pp$`1`)

```



## Scene 3


**Prompt:**  President Kenyatta has another question:

*I care more about increasing registration in poor communities. For a community with poverty_n equal to 2, what would you expect the change in registration under treatment to be?*

Using the model which you created in Scene 1, create a graphic of the posterior probability distribution of the causal effect of `local` treatment in polling stations which have +2 sigma poverty rates. Note that there are two ways to do this. First, we can use a parameter approach. This is what we did in class last week. Second, we can use `posterior_epred()`, which is generally easier since it does the math for us. Use the `posterior_epred()` approach. 

whts the diff bw an indiidual level of prediction and a range of expectation 
```{r}

newobs2 <- tibble(treatment = c("local", "control"), poverty_n = 2)
  
  
pe <- posterior_epred(fit, newdata = newobs2) %>%
  as_tibble() %>%
  mutate_all(as.numeric) %>%
  mutate(ce = `1` - `2`)

pe %>%
  ggplot(aes(ce)) +
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 alpha = 0.5,
                 bins = 100,
                 color = "darkslateblue",
                 fill = "lavender") +
  labs(title = "Posterior Probabiloity Distribution for Causal Effect of Treatment",
       subtitle = "for local reisrtation at polling stations in poor communities",
       x = "Expected Change in Registration ",
       y = "Probability") +
  scale_x_continuous(labels=scales::percent_format(accuracy = 1)) +
  scale_y_continuous(labels=scales::percent_format(accuracy = 1)) + 
  theme_classic()



```


